Power simulation section

### 2023-08-18 docs/manuscript.Rmd
fix small problem with future reference

Power analysis can quickly become computationally intensive, when we repeatedly simulate data and fit models for different parameter combinations or sample sizes.
Thus, we use the future [@R-future] and furrr [@R-furrr] packages to perform computations in parallel.
First, we enable parallelization and specify how many parallel cores of our computer to use (users can find out the maximum number of cores on their computer with the command `parallel::detectCores()`), and set a seed to make the simulation reproducible.

@@

For our exemplary combined hypothesis, power is defined as the (long-run) percentage of simulations, in which all four p-values of our component hypotheses are significant at the $\alpha = 0.05$ level.
Based on our simulation outcomes, we compute a power estimate for each combination of `n_subjects` $\times$ `n_items` (including 95% confidence intervals) and visualize the results with the following code [^faux].

>>>>

Power analysis can quickly become computationally intensive, when we repeatedly simulate data and fit models for different parameter combinations or sample sizes.
Thus, we use the future [@R-RJ-2021-048] and furrr [@R-furrr] packages to perform computations in parallel.
First, we enable parallelization and specify how many parallel cores of our computer to use (users can find out the maximum number of cores on their computer with the command `parallel::detectCores()`), and set a seed to make the simulation reproducible.

@@

For our exemplary combined hypothesis, power is defined as the (long-run) percentage of simulations, in which all four p-values of our component hypotheses are significant at the $\alpha = 0.05$ level.
Based on our simulation outcomes, we compute a power estimate for each combination of `n_subjects` $\times$ `n_items` (including 95% confidence intervals) and visualize the results with the following code.[^faux]
